### 2014-10-01 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Minor edits

\begin{enumerate}
\item For the initial couch fire in the basement, the HRR from 0~s to 327~s followed the experimentally measured mattress HRR. The HRR at 300~s was approximately 3~MW, and the HRR at 327~s was approximately 5~MW. From 327~s until 540~s (the end of the simulation), the HRR of the initial couch item was specified as a constant 5~MW.

@@

Figure~\ref{fig:timeline_comparison_rear} shows a time series comparison of on-scene photographs and Smokeview snapshots of flaming combustion that occured through the failed windows on the rear side of the structure. In this figure, the first photograph is shown at a simulation time of 321~s (approximately 20~s before the first rear basement window failed), the second photograph is shown at a simulation time of 349~s (approximately 10~s after the first rear basement window failed), the third photograph is shown at a simulation time of 440~s (approximately when the third rear basement window failed), and the fourth photograph is shown at a simulation time of 450~s (approximately when all of the rear basement windows failed). Figure~\ref{fig:timeline_comparison_front} shows a comparison of an on-scene photograph and Smokeview snapshot of smoke coming out of the front side of the structure at approximately the time when the rear windows began to fail.

>>>>

\begin{enumerate}
\item For the initial couch fire in the basement, the HRR from 0~s to 327~s followed the experimentally measured mattress HRR~\cite{madrzykowski2009fire}. The HRR at 300~s was approximately 3~MW, and the HRR at 327~s was approximately 5~MW. From 327~s until 540~s (the end of the simulation), the HRR of the initial couch item was specified as a constant 5~MW.

@@

Figure~\ref{fig:timeline_comparison_rear} shows a time series comparison of on-scene photographs and Smokeview snapshots of flaming combustion that occurred through the failed windows on the rear side of the structure. In this figure, the first photograph is shown at a simulation time of 321~s (approximately 20~s before the first rear basement window failed), the second photograph is shown at a simulation time of 349~s (approximately 10~s after the first rear basement window failed), the third photograph is shown at a simulation time of 440~s (approximately when the third rear basement window failed), and the fourth photograph is shown at a simulation time of 450~s (approximately when all of the rear basement windows failed). Figure~\ref{fig:timeline_comparison_front} shows a comparison of an on-scene photograph and Smokeview snapshot of smoke coming out of the front side of the structure at approximately the time when the rear windows began to fail.
